### 2016-12-31 Plos-one-manuscript/latex/manuscript.tex
working on manuscript

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjuseted to any discrete volume within range.
In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our desing does not use a membrane that may wear out and require tedious replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.

@@

>>>>

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjuseted to any discrete volume within range.
In addition the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our desing does not use a membrane that may wear out and require tedious replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a propriatiery software.

@@

\section*{Conclusion}
We have presented an open design micropipette that uses 3D-printable parts in addition to a disposable syringe and a few eaisly sourced pieces of hardware.
Our open design pipette is novel in that it allows the user to set the pipette to the desired volume with out the need to calibrate or verify with a weighing scale. 
We validated the accuracy and presiion of our pipette and developed a new graduation scale to correct for the use of the syringe for air-displacemet measurements.
o meet the ISO standard for adjustable pipettes.
Our design is free to use and modifiy to encourage further collabrateive developlement.
